Flatiron analysis

### 2021-03-25 Rmd/Report analysis update.Rmd
New analysis report

## Clinical summary table
```{r analysis_data}
analysis_data <- Frontline %>% 
  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

@@

```{r Table 3}
tbl1 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           "chemotherapy_type", "therapy", "mean_RDI_per_drug_chemotype", "RDI_grp")) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           "chemotherapy_type", "therapy", "treatment_sequence", "mean_RDI_per_drug_chemotype", "RDI_grp")) %>% 
  tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p()
tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```

@@

@@

tbl_stack(list(tbl3, tbl4, tbl5, tbl6))
```
<br>

@@

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by race
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by race
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

tbl1 <- analysis_data %>% 
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- tbl1 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl2 <- analysis_data %>% 
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
tbl2 <- tbl2 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl3 <- analysis_data %>% 
  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
tbl3 <- tbl3 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>% 
  bold_labels() %>%
  italicize_levels()
# Platin
tbl4 <- analysis_data %>% 
  filter(str_detect(drugname,"platin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- tbl4 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl5 <- analysis_data %>% 
  filter(str_detect(drugname,"platin") & chemotherapy_type == "Adjuvant")
tbl5 <- tbl5 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl6 <- analysis_data %>% 
  filter(str_detect(drugname,"platin") & str_detect(chemotherapy_type, "Chemo"))
tbl6 <- tbl6 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("platin/Neoadjuvant", "platin/Adjuvant", "platin/Chemo only")) %>% 
  bold_labels() %>%
  italicize_levels()

@@

tbl10 <- analysis_data %>% 
  filter(str_detect(drugname, "paclitaxel") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl11 <- analysis_data %>% 
  filter(str_detect(drugname, "paclitaxel") & chemotherapy_type == "Adjuvant")
tbl11 <- tbl11 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
  tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl12 <- analysis_data %>% 
  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
tbl12 <- tbl12 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl10, tbl11, tbl12),
          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>% 
  bold_labels() %>%
  italicize_levels()
```

@@

`glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)`
```{r}
# Regression RDI prediction
model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

### By drug
```{r}
#  for carbo
model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

@@

@@

## Plots for first treatment
For RDI, it is calculated for neoadjuvant and adjuvant when a patient got both.
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

@@

analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= RDI_grp1, fill = drugname))+
  geom_bar()+
  theme_minimal()+
  coord_flip()
```
</div>

@@

analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= RDI_grp1, fill = drugname))+
  geom_bar(position = "fill")+
  theme_minimal()+
  coord_flip()
```
</div>
</div>

>>>>

## Clinical summary table
```{r analysis_data}
analysis_data <- Frontline %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

@@

```{r Table 3}
tbl1 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p()
tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```

@@

tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl5 <- 
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl6 <- 
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl_stack(list(tbl4, tbl3, tbl5, tbl6))

@@

tbl_stack(list(tbl5, tbl6))
```
<br>

@@

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by race
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by race
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

tbl1 <- analysis_data %>% 
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- tbl1 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl2 <- analysis_data %>% 
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
tbl2 <- tbl2 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl3 <- analysis_data %>% 
  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
tbl3 <- tbl3 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>% 
  bold_labels() %>%
  italicize_levels()
# Cisplatin
tbl4 <- analysis_data %>% 
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- tbl4 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl5 <- analysis_data %>% 
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
tbl5 <- tbl5 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl6 <- analysis_data %>% 
  filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
tbl6 <- tbl6 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>% 
  bold_labels() %>%
  italicize_levels()

@@

tbl10 <- analysis_data %>% 
  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl11 <- analysis_data %>% 
  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
tbl11 <- tbl11 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
  tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl12 <- analysis_data %>% 
  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
tbl12 <- tbl12 %>% 
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl10, tbl11, tbl12),
          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>% 
  bold_labels() %>%
  italicize_levels()
```

@@

`glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)`
!!!! Prediction of RDI all drug together!!!!
```{r}
# Regression RDI prediction
model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

### By drug
!!! But sometimes we had a switch between cisplatin/carboplatin
```{r}
#  for carbo
model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

@@

#  for Cisplatim
model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
               filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
               filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

@@

## Plots for first treatment
For RDI, it is calculated for neoadjuvant and adjuvant when a patient got both.
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>%
  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

@@

```
</div>

@@

```
</div>
</div>

<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= RDI_grp1, fill = drugname))+
  geom_bar()+
  theme_minimal()+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
  # filter(linenumber_new == "1") %>% 
  ggplot(aes(x= RDI_grp1, fill = drugname))+
  geom_bar(position = "fill")+
  theme_minimal()+
  coord_flip()
```
</div>
</div>

<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->

<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->

<!-- ``` -->
<!-- </div> -->
<!-- </div> -->
